\documentclass{resume_en}

\usepackage{ctex}
\usepackage{float}
\usepackage{tabularx}

\author{Lu\ \ Chu}
\address{East China Normal University, No.3663 North Zhongshan Road, Shanghai}
\phone{(+86) 189-6107-3286}
\email{luchu1993@163.com}
\extras{
	Github: \href{https://github.com/luchu1993}{luchu1993}
}
\begin{document}
\maketitle

\TechnicalSkills
\begin{table}[H]
	\centering
	\begin{tabularx}{\textwidth}{X X X}
         \textbf{Programming Language} & \textbf{Software}  & \textbf{Machine Learning}\\
		\begin{itemize}
			\item C/C++
			\item Python
			\item Qt/QML
		\end{itemize} &
		\begin{itemize}
			\item Latex
			\item Git
			\item Linux/MacOS
		\end{itemize} &
        \begin{itemize}
            \item pytorch
            \item Tensorflow/Keras
            \item sklearn
        \end{itemize}
	\end{tabularx}
\end{table}
\vspace{-4em} % Ugly hack for spacing
\Education

\School{East China Normal University\ \ \ \ School of Computer Science and Software Engineering}{July, 2019}{Mater -- Cryptography and Cyber Security}
\School{ChangShu Institute of Technology\ \ \ \ School of Computer Science and Engineering}{July, 2015}{Bachelor -- Internet of Things}


\TechnicalProjects
%----------------科研项目---------------------------
\TechnicalProject{Group Attributes Context-aware Password Guessing Scheme}{November, 2017 -- Present}
\begin{itemize}
	\item Analyzed the defects and shortcomings of traditional password attack algorithms(PCFG and Markov).
	\item Proposed a weak password guessing method based on deep recurrent neural network.
    \item Combining user group attributes, we proposed a conditional RNN targeted weak password guessing technique.
    \item Performing related experiments on leaked password sets such as Rockyou, CSDN, and 12306, and we analyzed the experimental results.
\end{itemize}

\TechnicalProject{Generative Adversarial Networks Based Industrial Control System Protocol Reconstruction}{September, 2017 -- October, 2017}
\begin{itemize}
	\item Analyzed the necessity of reconstruction of industrial control protocols in fog computing scenarios.
	\item Convert industrial control protocols to gray scale images and analyze protocol features.
	\item Reconstruction of Industrial Control Protocol using DCGAN.
\end{itemize}

\TechnicalProject{An Adversarial Sample Based Attack Method for Malware Detection } {April, 2017 -- August, 2017}
\begin{itemize}
	\item Analyzed the problem of confrontational samples facing deep learning and traditional machine learning.
	\item Proposed a technique based on genetic algorithm to efficiently find the adversarial samples.
    \item Performed related experiments and analysis in malicious PDF file detection system.
\end{itemize}

\StudentTeams
\StudentTeam{Student Council Minister}{July, 2017 -- Present}
\begin{itemize}
	\item Organized the promotion and planning of student union activities.
	\item Organized academic activities.
\end{itemize}

\StudentTeam{Teaching Assistant}{September, 2017 -- January, 2018}
\begin{itemize}
    \item Participated in the teaching of computer programming courses.
    \item Assisted the teacher to complete the Q\&A work.
\end{itemize}

\OtherWorkExperience

\Job{Pioneer Suntec(ShangHai) Electronic Technology Co., Ltd}{January, 2015 -- July, 2015}{C++ Programmer}
\begin{itemize}
	\item Participated in the development of embedded software for in-vehicle electronic systems.
	\item Maintaining related documents and learn to use QML.
\end{itemize}

\Job{Suzhou C2fun Network Technology Co., Ltd}{September, 2015 -- March, 2016}{Game Developer}
\begin{itemize}
	\item Participate in "Three Kingdoms" development work.
	\item Participate in the optimization and development of the company's game engine.
\end{itemize}


\Intrests

\begin{itemize}
	\item Reading -- I like Wang Xiaobo's "The Golden Age", Yu Hua's "Living", and Zhang Yueran's "The Skull".
	\item Algorithm -- I like to study machine learning and like to read Bishop's classic book "Patter Recognition and Machine Learning". I also shared my reading notes, please refer to my github.
    \item Sports -- Pingpong, badminton.
\end{itemize}

\end{document}
